\tool: Programmable and Efficient Secure Two-Party Computation for Machine Learning

### 2018-08-07 ndss/ex.tex
pass

Within the secret components, the \tool compiler is ``cryptographic
cost-aware'', and appropriately picks either arithmetic or boolean
circuit representations for different sub-components. For example,
the compiler realizes that the inner product computation is more
efficient in the arithmetic representation, and therefore it builds
the corresponding circuit using the arithmetic circuit builder
\ls{acirc} (lines~\ref{line:dotmulgate} and~\ref{line:dotaddgate}). On
the other hand, since the comparison with \ls{b}, and the conditional
expression (the '? :' operator) computation are more efficient in the
boolean representation, the \tool compiler uses the Yao circuit
builder \ls{ycirc} to build the corresponding comparison and
multiplexer circuits
(lines~\ref{line:condyaobegin} to~\ref{line:condyaoend}) (in our usage
of ABY, boolean is synonymous with Yao, we elaborate in
\sectionref{impl}).

@@

We have evaluated against handwritten ABY code for the examples in the ABY repository and \tool has comparable performance. However, these examples are not representative of practical ML tasks. Writing sophisticated ML applications such as neural networks in ABY is a very tedious and nearly impossible engineering task even for crypto experts -- automating the same is our main contribution.

@@

\section{Cryptographic cost-awareness}
 \label{sec:ccc}
In this section, we explain various heuristics that \tool uses to split
the computation in a program into arithmetic and
boolean parts. Since finding an optimum split  is an NP-hard problem (the predicates in {\tt if} statements can have arbitrary non-linear arithmetic),
\tool uses heuristics  that  perform well in practice (Section~\ref{sec:eval}).

The split
between arithmetic and boolean requires knowing the cost of
individual operations
(addition, multiplication, inter-conversion between arithmetic and boolean, etc.).
Demmler
et al.~\cite{aby} document these costs by running
microbenchmarks for basic operations and interconversions (Figures
2 and 3 in \cite{aby}). \tool heuristics are based on their results.

@@

For multiplication, \tool always chooses
an arithmetic circuit, as the cost of a boolean multiplication is much
higher than the cost of converting the operands from boolean to
arithmetic, performing an arithmetic multiplication, and then converting
the result back to boolean ($\sim9x$ more time $\&$ $\sim20x$ more
communication in a LAN setting). The size of a boolean multiplication circuit is quadratic in the bit-width, which causes this performance gap.
Roughly, multiplying two $64$-bit integers using arithmetic sharing requires only $2$ multiplications, whereas Yao requires at least $4096$ AES operations in the online phase.
Since this gap is quite large, we believe that this choice is optimal for realistic network
settings. Finally, \tool chooses boolean circuits for all
the operations lacking arithmetic support in ABY, e.g., comparisons, bit-shifts, etc.
Further implementation details can be found in~\sectionref{impl}.

>>>>

Within the secret components, the \tool compiler is ``cryptographic
cost-aware'', and appropriately picks either arithmetic or boolean
circuit representations for different sub-components. For example,
the compiler realizes that the inner product computation is more
efficient in the arithmetic representation, and therefore it builds
the corresponding circuit using the arithmetic circuit builder
\ls{acirc} (lines~\ref{line:dotmulgate} and~\ref{line:dotaddgate}). On
the other hand, since the comparison with \ls{b}, and the conditional
expression (the '? :' operator) computation are more efficient in the
boolean representation, the \tool compiler uses the Yao circuit
builder \ls{ycirc} to build the corresponding comparison and
multiplexer circuits
(lines~\ref{line:condyaobegin} to~\ref{line:condyaoend}). In our usage
of ABY, boolean is synonymous with Yao, we elaborate in
\sectionref{impl}.

@@

We have evaluated against handwritten ABY code for the examples in the
ABY repository and \tool has comparable performance. However, these
examples are not representative of practical ML tasks. Writing
sophisticated ML applications such as neural networks in ABY is a very
tedious and nearly-impossible engineering task even for crypto experts
-- automating the same is our main contribution.

@@

\section{Cryptographic cost awareness}
 \label{sec:ccc}
In this section, we explain various heuristics that \tool uses to split
the computation in a program into arithmetic and
boolean parts. Since finding an optimum split  is an NP-hard problem (the predicates in {\tt if} statements can have arbitrary non-linear arithmetic),
\tool uses heuristics  that  perform well in practice (Section~\ref{sec:eval}).

The split
between arithmetic and boolean requires knowing the cost of
individual operations
(addition, multiplication, interconversion between arithmetic and boolean, etc.).
Demmler
et al.~\cite{aby} document these costs by running
microbenchmarks for basic operations and interconversions (Figures
2 and 3 in \cite{aby}). \tool heuristics are based on their results.

@@

For multiplication, \tool always chooses
an arithmetic circuit, as the cost of a boolean multiplication is much
higher than the cost of converting the operands from boolean to
arithmetic, performing an arithmetic multiplication, and then converting
the result back to boolean ($\sim9x$ more time $\&$ $\sim20x$ more
communication in a LAN setting). The size of a boolean multiplication circuit is quadratic in the bit-width, which causes this performance gap.
Roughly, multiplying two $64$-bit integers using arithmetic sharing requires only $2$ multiplications, whereas Yao requires at least $4096$ AES operations in the online phase.
Since this gap is quite large, we believe that this choice is optimal for realistic network
settings. Finally, \tool chooses boolean circuits for all
the operations lacking arithmetic support in ABY, e.g. comparisons, bit-shifts, etc.
We provide more implementation details in~\sectionref{impl}.

### 2018-08-07 ndss/intro.tex
pass

Alternatively, Alice can use a tool such as ABY (Demmler et
al.~\cite{aby}) that allows
the computation to be expressed as a combination of arithmetic and
boolean circuits. However, here, the programming interface is quite
low-level: the programmer is required to first manually split the
computation into arithmetic and boolean components, and then write the
circuits for all the components manually, including the appropriate
inter-conversion gates between them. Clearly, writing correct
and efficient protocols in such a framework is beyond an average
programmer who does not understand the various trade-offs between
arithmetic and boolean circuits, and even for an expert cryptographer,
writing large computations in such a framework can be tedious (a sentiment echoed by Demmler et al.~\cite{aby} themselves).

@@

\subsection{Our Contributions}
This paper presents \tool\footnote{Read as ``easy peasy'',
stands for Easy 2 Party Computation.}, the first
``cryptographic-cost aware'' compiler that generates efficient and
scalable \mpc protocols using combinations of
arithmetic and boolean circuits. \tool source language is a simple
imperative language absent of any cryptographic details. The compiler
is
backed by a formal model
that enables it to choose arithmetic or boolean representations for
different parts of
the program, while automatically inserting inter-conversion gates as
necessary. In addition to guiding the compiler, the formal model also
provides strong correctness and
security theorems. Our comprehensive evaluation shows that the
automatically generated protocols have performance comparable to
or better than the custom, specialized
protocols from previous works~\cite{shafindss,wu,minionn,secureml,cryptonets,valeriaMatrix}.
In fact, these papers (and others) cite the inefficiency of generic \mpc as the major motivation
behind the design of specialized protocols. Using \tool, we empirically  demonstrate
that generic \mpc implementations are much more efficient than what they were believed to be. 
Below we describe
the salient features of \tool.

%% that introduce unique compilation challenges.
%% Standard compilers do not attempt to reason about or insert non-trivial type casts
%% and require the programmers to perform them explicitly. \aseem{This
%% last sentence and the bit about unique compilation challenges seems
%% unnecessary to me. Compilers do insert type casts automatically. Also
%% at this point in the paper the words ``type casts'' don't mean much.}
%% We back \tool with formal semantics that enable the compiler to
%% insert type conversions between boolean and arithmetic components
%% while maintaining provable correctness, security, and
%% efficiency. \aseem{Provable efficiency? Perhaps provable should
%% be rescoped. And again, type conversions may not be clear at this
%% point. I would simply say that EzPC inserts inter-conversion gates
%% automatically. It is backed by a formal model and provides
%% provable correctness and security, and efficiency.}

%% This paper presents \tool\footnote{Read as ``easy peasy'',
%% stands for Easy 2 Party Computation.}, the first
%% ``cryptographic-cost aware'' framework that generates efficient and
%% scalable \mpc protocols from high-level programs devoid of any
%% cryptographic details. 
%% The generated protocols use combinations of
%% arithmetic and boolean circuits that introduce unique compilation challenges.
%% Standard compilers do not attempt to reason about or insert non-trivial type casts
%% and require the programmers to perform them explicitly. \aseem{This
%% last sentence and the bit about unique compilation challenges seems
%% unnecessary to me. Compilers do insert type casts automatically. Also
%% at this point in the paper the words ``type casts'' don't mean much.}
%% We back \tool with formal semantics that enable the compiler to
%% insert type conversions between boolean and arithmetic components
%% while maintaining provable correctness, security, and
%% efficiency. \aseem{Provable efficiency? Perhaps provable should
%% be rescoped. And again, type conversions may not be clear at this
%% point. I would simply say that EzPC inserts inter-conversion gates
%% automatically. It is backed by a formal model and provides
%% provable correctness and security, and efficiency.}
%% The automatically generated protocols have performance comparable to
%% or better than the custom, specialized
%% protocols from previous works~\cite{shafindss,wu,minionn,secureml,cryptonets,valeriaMatrix}.
%% In fact, these papers (and others) cite the inefficiency of generic \mpc as the major motivation
%% behind the design of specialized protocols. Using \tool, we empirically  demonstrate
%% that generic \mpc implementations are much more efficient than what they were believed to be. 
%%  %(up to a factor of 19x in our
%% %experiments, depending on the functionality) \nc{I added this but I
%% %  guess we are saying it many times, but might be nice to highlight
%% %  perf early no?} \aseem{My rationale was to save the numbers for
%% %  Evaluation summary and remain high-level here.} 
%% Below we describe
%% the salient features of \tool.

@@

\subsubsection{Cryptographic-cost aware compiler} The \tool compiler
compiles a source program to a hybrid computation consisting
of \emph{public} and \emph{secret} parts. In the example above, for
instance, \tool compiler realizes that the array index~\ls{i} is
public, and generates non-cryptographic code for the array accesses.
Further, within the secret parts, \tool compiler is
aware
of the cryptographic costs of arithmetic and boolean representations
of the source language operators. Based on these costs, the compiler
automatically picks arithmetic or boolean
representations for different sub-parts, and generates the
corresponding circuits along with the required inter-conversion
gates. The outcome is an efficient \mpc protocol combining arithmetic
and boolean circuits, while the programmer remains
oblivious of all these cryptographic details. Indeed, \tool is the
first such cryptographic-cost aware compiler.

\subsubsection{Scalability (secure code partitioning)} \mpc tools
often do not scale to large functionalities. The reason is that
most \mpc implementations use a circuit-like representation as an
intermediate language. Hence, the largest compute that can be done
securely is upper-bounded by the largest circuit that can fit in the
machine memory\footnote{Using swap and
disk space is feasible but it causes huge slowdown.}. This is a
show-stopper for applications like secure machine learning, secure
prediction, etc. that operate on large data.
%\aseem{Can we
%cite something here to support this claim?}
\tool addresses the scalability concern using a novel technique that
we call secure code partitioning (or partitioning in short). At
a high level, we decompose the original program into a sequence of small
sub-programs, which are then sequentially processed by \tool, while
appropriately threading the intermediate outputs
along. While this
addresses the scalability concern (i.e., the circuit
sizes of the sub-programs are now small enough to fit in the memory),
we still have to address
the security risk of revealing the intermediate outputs. \tool comes
to the rescue; it automatically inserts the required instrumentation
to ensure security of these intermediate outputs (\sectionref{pipe}). As
we show in our
evaluation, partitioning allows us to program large applications
in \tool. 
%\aseem{What about the differences from Yao pipelining? Worth
%adding here that it is a backend-agnostic technique?}

@@

\subsubsection{Formal guarantees} We prove formal correctness and
security theorems for our compiler. The correctness theorem relates the
``trusted third party'' semantics of a source
program and the ``protocol'' semantics (the distributed \mpc
semantics that relies on circuit evaluation) of the corresponding
compiled program. The theorem
guarantees that for all well-typed source programs, the two semantics
successfully terminate
(e.g., there are no array index out-of-bounds errors) with identical
observable outputs. For
the security theorem, we formally reduce the security
of our scheme against semi-honest (or ``honest but curious")
adversaries to the semi honest security of the  \mpc backend. The
theorem provides protection against side-channels arising from
conditionals and memory access patterns.
 We also prove a formal security theorem against semi-honest
 adversaries for our partitioning
scheme (\sectionref{ld} and~\sectionref{pipe}).

\subsubsection{Evaluation}We implemented \tool
using ABY~\cite{aby} as the
cryptographic backend.
We compare \tool with Yao-based compilers in~\sectionref{oblivm}
and with specialized protocols in~\sectionref{eval}. 
 We evaluate \tool by implementing a wide range
of secure prediction benchmarks including linear and na\"{i}ve bayes
classifiers, decision trees, deep neural networks, state-of-the-art
classifiers from Tensorflow~\cite{tensorflow}
and \bonsai~\cite{bonsai}, and also matrix factorization from Nikolaenko et al.~\cite{valeriaMatrix}. Our results demonstrate
three key points. First, \tool makes it convenient for general
programmers to write \mpc protocols. E.g. we provide the first \mpc
implementation of \bonsai~\cite{bonsai}, and it was programmed in the
high-level \tool source language by a non-cryptographer. Second, the
performance
of the protocols
generated by \tool are comparable to or better than (up to 19x) their state-of-the-art, hand-crafted implementations. Finally, we
demonstrate the usefulness of partitioning by implementing an application
that requires more than 300 million gates (\sectionref{impl} and~\sectionref{eval}).

>>>>

Alternatively, Alice can use a tool such as ABY (Demmler et
al.~\cite{aby}) that allows
the computation to be expressed as a combination of arithmetic and
boolean circuits. However, here, the programming interface is quite
low-level: the programmer is required to first manually split the
computation into arithmetic and boolean components, and then write the
circuits for all the components manually, including the appropriate
interconversion gates between them. Clearly, writing correct
and efficient protocols in such a framework is beyond an average
programmer who does not understand the various trade-offs between
arithmetic and boolean circuits, and even for an expert cryptographer,
writing large computations in such a framework can be tedious (a sentiment echoed by Demmler et al.~\cite{aby} themselves).

@@

\subsection{Our Contributions}
This paper presents \tool\footnote{Read as ``easy peasy'',
stands for Easy 2 Party Computation.}, the first
``cryptographic cost aware'' compiler that generates efficient and
scalable \mpc protocols using combinations of
arithmetic and boolean circuits. \tool source language is a simple
imperative language absent of any cryptographic details. The compiler
is
backed by a formal model
that enables it to choose arithmetic or boolean representations for
different parts of
the program, while automatically inserting interconversion gates as
necessary. In addition to guiding the compiler, the formal model also
provides strong correctness and
security theorems. Our comprehensive evaluation shows that the
automatically generated protocols have performance comparable to
or better than the custom, specialized
protocols from previous works~\cite{shafindss,wu,minionn,secureml,cryptonets,valeriaMatrix}.
In fact, these papers (and others) cite the inefficiency of generic \mpc as the major motivation
behind the design of specialized protocols. Using \tool, we empirically  demonstrate
that generic \mpc implementations are much more efficient than what they were believed to be. 
Below we describe
the salient features of \tool.

%% that introduce unique compilation challenges.
%% Standard compilers do not attempt to reason about or insert non-trivial type casts
%% and require the programmers to perform them explicitly. \aseem{This
%% last sentence and the bit about unique compilation challenges seems
%% unnecessary to me. Compilers do insert type casts automatically. Also
%% at this point in the paper the words ``type casts'' don't mean much.}
%% We back \tool with formal semantics that enable the compiler to
%% insert type conversions between boolean and arithmetic components
%% while maintaining provable correctness, security, and
%% efficiency. \aseem{Provable efficiency? Perhaps provable should
%% be rescoped. And again, type conversions may not be clear at this
%% point. I would simply say that EzPC inserts interconversion gates
%% automatically. It is backed by a formal model and provides
%% provable correctness and security, and efficiency.}

%% This paper presents \tool\footnote{Read as ``easy peasy'',
%% stands for Easy 2 Party Computation.}, the first
%% ``cryptographic-cost aware'' framework that generates efficient and
%% scalable \mpc protocols from high-level programs devoid of any
%% cryptographic details. 
%% The generated protocols use combinations of
%% arithmetic and boolean circuits that introduce unique compilation challenges.
%% Standard compilers do not attempt to reason about or insert non-trivial type casts
%% and require the programmers to perform them explicitly. \aseem{This
%% last sentence and the bit about unique compilation challenges seems
%% unnecessary to me. Compilers do insert type casts automatically. Also
%% at this point in the paper the words ``type casts'' don't mean much.}
%% We back \tool with formal semantics that enable the compiler to
%% insert type conversions between boolean and arithmetic components
%% while maintaining provable correctness, security, and
%% efficiency. \aseem{Provable efficiency? Perhaps provable should
%% be rescoped. And again, type conversions may not be clear at this
%% point. I would simply say that EzPC inserts interconversion gates
%% automatically. It is backed by a formal model and provides
%% provable correctness and security, and efficiency.}
%% The automatically generated protocols have performance comparable to
%% or better than the custom, specialized
%% protocols from previous works~\cite{shafindss,wu,minionn,secureml,cryptonets,valeriaMatrix}.
%% In fact, these papers (and others) cite the inefficiency of generic \mpc as the major motivation
%% behind the design of specialized protocols. Using \tool, we empirically  demonstrate
%% that generic \mpc implementations are much more efficient than what they were believed to be. 
%%  %(up to a factor of 19x in our
%% %experiments, depending on the functionality) \nc{I added this but I
%% %  guess we are saying it many times, but might be nice to highlight
%% %  perf early no?} \aseem{My rationale was to save the numbers for
%% %  Evaluation summary and remain high-level here.} 
%% Below we describe
%% the salient features of \tool.

@@

\subsubsection{Cryptographic cost aware compiler} The \tool compiler
compiles a source program to a hybrid computation consisting
of \emph{public} and \emph{secret} parts. In the example above, for
instance, \tool compiler realizes that the array index~\ls{i} is
public, and generates non-cryptographic code for the array accesses.
Further, within the secret parts, \tool compiler is
aware
of the cryptographic costs of arithmetic and boolean representations
of the source language operators. Based on these costs, the compiler
automatically picks arithmetic or boolean
representations for different sub-parts, and generates the
corresponding circuits along with the required interconversion
gates. The outcome is an efficient \mpc protocol combining arithmetic
and boolean circuits, while the programmer remains
oblivious of all these cryptographic details. Indeed, \tool is the
first such cryptographic cost aware compiler.

\subsubsection{Scalability (secure code partitioning)} \mpc tools
often do not scale to large functionalities. The reason is that
most \mpc implementations use a circuit-like representation as an
intermediate language. Hence, the largest compute that can be done
securely is upper-bounded by the largest circuit that can fit in the
machine memory\footnote{Using swap and
disk space is feasible but it causes huge slowdown (\figureref{partitioning}).}. This is a
show-stopper for applications like secure machine learning, secure
prediction, etc. that operate on large data.
%\aseem{Can we
%cite something here to support this claim?}
\tool addresses the scalability concern using a novel technique that
we call secure code partitioning (or partitioning in short). At
a high level, we decompose the original program into a sequence of small
sub-programs, which are then sequentially processed by \tool, while
appropriately threading the intermediate outputs
along. While this
addresses the scalability concern (i.e., the circuit
sizes of the sub-programs are now small enough to fit in the memory),
we still have to address
the security risk of revealing the intermediate outputs. \tool comes
to the rescue; it automatically inserts the required instrumentation
to ensure security of these intermediate outputs (\sectionref{pipe}). As
we show in our
evaluation, partitioning allows us to program large applications
in \tool. 
%\aseem{What about the differences from Yao pipelining? Worth
%adding here that it is a backend-agnostic technique?}

@@

\subsubsection{Formal guarantees} We prove formal correctness and
security theorems for our compiler. The correctness theorem relates the
``trusted third party'' semantics of a source
program and the ``protocol'' semantics (the distributed \mpc
semantics that relies on circuit evaluation) of the corresponding
compiled program. The theorem
guarantees that for all well-typed source programs, the two semantics
successfully terminate
(e.g., there are no array index out-of-bounds errors) with identical
observable outputs. For
the security theorem, we formally reduce the security
of our scheme against semi-honest (or ``honest but curious")
adversaries to the semi-honest security of the  \mpc backend. The
theorem provides protection against side-channels arising from
conditionals and memory access patterns.
 We also prove a formal security theorem against semi-honest
 adversaries for our partitioning
scheme (\sectionref{ld} and~\sectionref{pipe}).

\subsubsection{Evaluation}We implemented \tool
using ABY~\cite{aby} as the
cryptographic backend.
We compare \tool with Yao-based compilers in~\sectionref{oblivm}
and with specialized protocols in~\sectionref{eval}. 
 We evaluate \tool by implementing a wide range
of secure prediction benchmarks including linear and na\"{i}ve bayes
classifiers, decision trees, deep neural networks, state-of-the-art
classifiers from Tensorflow~\cite{tensorflow}
and \bonsai~\cite{bonsai}, and also matrix factorization from Nikolaenko et al.~\cite{valeriaMatrix}. Our results demonstrate
three key points. First, \tool makes it convenient for general
programmers to write \mpc protocols. E.g. we provide the first \mpc
implementation of \bonsai~\cite{bonsai}, and it was programmed in the
high-level \tool source language by a non-cryptographer. Second, the
performance
of the protocols
generated by \tool is comparable to or better than (up to 19x) their state-of-the-art, hand-crafted implementations. Finally, we
demonstrate the usefulness of partitioning by implementing an application
that requires more than 300 million gates (\sectionref{impl} and~\sectionref{eval}).

### 2018-08-07 ndss/ld.tex
pass

In this section we prove correctness and security of our \tool compiler.
The readers who are interested in using the compiler as a black box can
move directly to  Section~\ref{sec:pipe} without loss of continuity.
%\dg{Put a warning that this section is technical and not prerequisite for understanding later section.}
%We formalize our source, intermediate and circuit languages. 
%An example of a program in our source language is provided in \figureref{ex-sml}.
%Our source runtime semantics is a model of the ideal, trusted third-party semantics, and
%generates observations corresponding to the values revealed to the
%parties.
We first formalize our source language (an example program being
\figureref{ex-sml}), and its runtime semantics.
This semantics describes the ``trusted third party"
execution semantics of the source programs and
generates observations corresponding to the values revealed to the
parties.
%
We then present the compilation rules that type check a program in the
source language and generate a program in the intermediate
language (an example program being \figureref{ex-aby}).
%
Next, we present the runtime semantics of our intermediate language
that evaluates to a circuit by ``evaluating away'' the public parts
and the arrays. Crucially, this step does not have access to the secret
inputs; those are processed by our distributed circuit semantics that
model the \mpc backend.
%
Evaluation in this distributed setting involves the parties running an
interactive protocol. This step, like  the source semantics, emits
observations corresponding to the values revealed to the parties.
%Finally, we formalize the distributed circuit semantics (of the cryptographic backend) that computes the generated circuit in the distributed setting, and like  the source semantics, emits observationscorresponding to the values revealed to the parties.

To prove the correctness of \tool, we prove that  the observations in
source semantics and the distributed circuit semantics are identical
(\theoremref{correctness}).
We combine this correctness theorem and the security of the \mpc
backend to prove security of the protocols generated by \tool
(\theoremref{security}).
%For the security of our compiler, we rely on the correctness guarantee and  reduce the security to the security of the underlying cryptographic protocol used to compute the generated circuit (see \theoremref{security}).
We present only selected parts of our formalization. Full definitions, auxiliary lemmas and complete proofs (that follow from a straight-forward induction argument once the key lemmas are identified) can be found in the full version of this paper. %We will also
%release complete typeset proofs in a tech report.

@@

	\inferrule*[lab={\footnotesize{T-Read}}]
               {
                 \Gamma \vdash x : \sigma^{\ell}[n] \leadsto x\\\\
                 \Gamma \vdash e : \kw{uint}^{\mathcal{P}} \leadsto \widetilde{e}\\\\
                  \models e < n
               }
               {
                 \Gamma \vdash x[e] : \sigma^{\ell} \leadsto x[\widetilde{e}]
               }

@@

The judgment $\Gamma \vdash e : \tau \leadsto \widetilde{e}$, where
$\Gamma$ maps variables $x$ to types $\tau$, says that
under $\Gamma$, $e$ (in the source language) compiles to $\widetilde{e}$
(in the intermediate language), where $\widetilde{e}$ has type $\tau$.
Rules ({\sc{T-UInt}}) and ({\sc{T-Bool}}) assigns the label
$\mathcal{P}$ to the constants, as the constants are always
public. Rule ({\sc{T-Mult}})
compiles a multiplication to either a public multiplication  ($\mulop_{\mathcal{P}}$), or a
secret arithmetic multiplication ($\mulop_{\mathcal{A}}$). As
our compiler is cryptographic cost aware, it never compiles the
multiplication to boolean multiplication $\mulop_{\mathcal{B}}$ (\sectionref{impl}). In a similar manner,
rule ({\sc{T-Gt}}) compiles $e_{1} > e_{2}$ to either public comparison,
or secret boolean comparison $>_\mathcal{B}$ (and never
$>_{\mathcal{A}}$).
%
The rule for conditional
({\sc{T-Cond}}) has two cases: when the conditional expression $e$ is of
type $\kw{bool}^{\mathcal{P}}$, both the branches have a base type
$\sigma^{\ell_{1}}$, for an arbitrary $\ell_{1}$, and the conditional is
compiled to a public conditional, whereas when the conditional
expression has type $\kw{bool}^{\mathcal{B}}$, $\ell_{1}$ is also
$\mathcal{B}$, and the conditional is compiled to a secret conditional
using a boolean circuit. Note that we restrict the type of the branches
to be of base type. 
Rule ({\sc{T-Read}}) type checks an array read. It checks
that the array index $e$ is public, and uses a static bounds checking
judgment $ \models e < n$ to prove that the array index is in
bounds \footnote{\sectionref{impl} discusses our implementation of this
check.}. Secret dependent array accesses can be encoded using the
conditional expressions (see Section~\ref{sec:impl}).  Rule
({\sc{T-Inp}}) picks a label
$m$ for the input. Finally,
the rule ({\sc{T-Sub}}) is the subsumption rule that coerces an expression of
type $\sigma^{\ell}$ to an expression of type $\sigma^{m}$ using the
coerce expression. It is important for security that the secrets
cannot be coerced to public values and indeed ({\sc{T-Sub}}) does not
permit it.

>>>>

In this section we prove correctness and security of the \tool compiler.
The readers who are interested in using the compiler as a black box can
move directly to  Section~\ref{sec:pipe} without loss of continuity.
%\dg{Put a warning that this section is technical and not prerequisite for understanding later section.}
%We formalize our source, intermediate and circuit languages. 
%An example of a program in our source language is provided in \figureref{ex-sml}.
%Our source runtime semantics is a model of the ideal, trusted third-party semantics, and
%generates observations corresponding to the values revealed to the
%parties.
We first formalize our source language (an example program being
\figureref{ex-sml}), and its runtime semantics.
This semantics describes the ``trusted third party"
execution semantics of the source programs and
generates observations corresponding to the values revealed to the
parties.
%
We then present the compilation rules that type check a program in the
source language and generate a program in the intermediate
language (an example program being \figureref{ex-aby}).
%
Next, we present the runtime semantics of our intermediate language
that evaluates to a circuit by ``evaluating away'' the public parts
and the arrays. Crucially, this step does not have access to the secret
inputs; those are processed by our distributed circuit semantics that
model the \mpc backend.
%
Evaluation in this distributed setting involves the parties running an
interactive protocol. This step, like  the source semantics, emits
observations corresponding to the values revealed to the parties.
%Finally, we formalize the distributed circuit semantics (of the cryptographic backend) that computes the generated circuit in the distributed setting, and like  the source semantics, emits observationscorresponding to the values revealed to the parties.

To prove the correctness of \tool, we prove that  the observations in
source semantics and the distributed circuit semantics are identical
(\theoremref{correctness}).
We combine this correctness theorem and the security of the \mpc
backend to prove security of the protocols generated by \tool
(\theoremref{security}).
%For the security of our compiler, we rely on the correctness guarantee and  reduce the security to the security of the underlying cryptographic protocol used to compute the generated circuit (see \theoremref{security}).
We present only selected parts of our formalization. Full definitions,
auxiliary lemmas, and complete proofs (that follow from a
straightforward induction argument once the key lemmas are
identified) can be found in the full version of this paper. %We will
                                %also
%release complete typeset proofs in a tech report.

@@

	\inferrule*[lab={\footnotesize{T-Read}}]
               {
                 \Gamma \vdash x : \sigma^{\ell}[n] \leadsto x\\\\
                 \Gamma \vdash e : \kw{uint}^{\mathcal{P}} \leadsto \widetilde{e}\\\\
                 \Gamma \models e < n
               }
               {
                 \Gamma \vdash x[e] : \sigma^{\ell} \leadsto x[\widetilde{e}]
               }

@@

The judgment $\Gamma \vdash e : \tau \leadsto \widetilde{e}$, where
$\Gamma$ maps variables $x$ to types $\tau$, says that
under $\Gamma$, $e$ (in the source language) compiles to $\widetilde{e}$
(in the intermediate language), where $\widetilde{e}$ has type $\tau$.
Rules ({\sc{T-UInt}}) and ({\sc{T-Bool}}) assigns the label
$\mathcal{P}$ to the constants, as the constants are always
public. Rule ({\sc{T-Mult}})
compiles a multiplication to either a public multiplication  ($\mulop_{\mathcal{P}}$), or a
secret arithmetic multiplication ($\mulop_{\mathcal{A}}$). As
our compiler is cryptographic cost aware, it never compiles the
multiplication to boolean multiplication $\mulop_{\mathcal{B}}$ (\sectionref{impl}). In a similar manner,
rule ({\sc{T-Gt}}) compiles $e_{1} > e_{2}$ to either public comparison,
or secret boolean comparison $>_\mathcal{B}$ (and never
$>_{\mathcal{A}}$).
%
The rule for conditional
({\sc{T-Cond}}) has two cases: when the conditional expression $e$ is of
type $\kw{bool}^{\mathcal{P}}$, both the branches have a base type
$\sigma^{\ell_{1}}$, for an arbitrary $\ell_{1}$, and the conditional is
compiled to a public conditional, whereas when the conditional
expression has type $\kw{bool}^{\mathcal{B}}$, $\ell_{1}$ is also
$\mathcal{B}$, and the conditional is compiled to a secret conditional
using a boolean circuit. Note that we restrict the type of the branches
to be of base type. 
Rule ({\sc{T-Read}}) type checks an array read. It checks
that the array index $e$ is public, and uses a static bounds checking
judgment $\Gamma \models e < n$ to prove that the array index is in
bounds \footnote{\sectionref{impl} discusses our implementation of this
check.}. Secret dependent array accesses can be encoded using the
conditional expressions (see Section~\ref{sec:impl}).  Rule
({\sc{T-Inp}}) picks a label
$m$ for the input. Finally,
the rule ({\sc{T-Sub}}) is the subsumption rule that coerces an expression of
type $\sigma^{\ell}$ to an expression of type $\sigma^{m}$ using the
coerce expression. It is important for security that the secrets
cannot be coerced to public values and indeed ({\sc{T-Sub}}) does not
permit it.

### 2018-08-07 ndss/pipe.tex
pass

In this section, we describe our ``secure code partitioning'' technique that
allows \tool to execute programs that require large circuits. The reason to implement partitioning is as follows: when compiling from a high level functionality to a circuit being evaluated securely, the circuits so generated can quite often be larger than the total memory available on the machines executing 2PC. The secure protocol for evaluating this circuit cannot then be generated without swapping the circuit in and out of main memory, thereby causing large slowdowns (see Section \ref{sec:pipeeval}). In order to avoid this problem, we ``split'' the high level functionality into smaller programs that compile into small circuits whose secure evaluation can completely fit into main memory. These smaller circuits are then evaluated sequentially to evaluate the entire program. Naturally, care must be taken to ensure that the partial evaluation of these circuits do not reveal any more information than the final output of the overall functionality. More details follow.

>>>>

In this section, we describe our ``secure code partitioning'' technique that
allows \tool to execute programs that require large circuits. The
reason to implement partitioning is as follows: when compiling from a
high level functionality to a circuit, the generated circuits
can quite often be larger than the total memory
available on the machines executing 2PC. The secure protocol for
evaluating this circuit cannot then be generated without swapping the
circuit in and out of main memory, thereby causing large slowdowns
(see Section \ref{sec:pipeeval}). In order to avoid this problem, we
``split'' the high level functionality into smaller programs that
compile into small circuits whose secure evaluation can completely fit
into main memory. These smaller circuits are then evaluated
sequentially to evaluate the entire program. Naturally, care must be
taken to ensure that the partial evaluation of these circuits do not
reveal any more information than the final output of the overall
functionality. More details follow.
